### 2018-08-23 doc/paper.tex
Slimming down the introduction.
Removing three figures and the overly simply method of
characteristics explanation.

\begin{figure}
  \includegraphics{simple_transport.pdf}
  \centering
  \captionsetup{width=.75\linewidth}
  \caption{The solution to \(u_t + u_x = 0, \; u(x, 0) = x^3\) plotted in
    the \(xu\)-plane. Demonstrates simple transport of
    the solution.}
  \label{fig:simple-transport}
\end{figure}

The method of characteristics helps transform partial differential equations
into ordinary differential equations by dividing the physical domain into
a family of curves. For example, the simple transport equation
\begin{equation}\label{eq:simple-transport}
u_t + c u_x = 0
\end{equation}
can be transformed when restricting to the family of lines
\(x(t) = x_0 + c t\). On these lines \(u(x(t), t)\) is constant, by
construction, and so the solution is ``transported'' from \(u(x_0, 0)\)
along each characteristic line (Figure~\ref{fig:simple-transport}).

Motivated by this, \emph{Lagrangian methods} treat each point in the
physical domain as a ``particle'' which moves along a characteristic curve
over time and then monitor values associated with the particle (heat / energy,
velocity, pressure, density, concentration, etc.). They are an effective way
to solve PDEs, even with higher order or non-linear terms.
For example, if a diffusion term is added to~\eqref{eq:simple-transport}
\begin{equation}
u_t + c u_x - \eps u_{xx} = 0
\end{equation}
then the same characteristics can be used, but the value
along each characteristic is no longer constant; instead it satisfies the
ODE \(\frac{d}{dt} u(x(t), t) = \eps u_{xx}\).

@@

\begin{figure}
  \includegraphics{distortion_remesh.pdf}
  \centering
  \captionsetup{width=.75\linewidth}
  \caption{Remeshing a domain after distortion caused by particle motion
    along the velocity field \(\left[ y^2 \; 1 \right]^T\) from \(t = 0\)
    to \(t = 1\).}
  \label{fig:distortion-remesh}
\end{figure}

To deal with distortion, one can allow the mesh to adapt in between time
steps. For example, Figure~\ref{fig:distortion-remesh} shows an example
remeshing of the domain.
In addition to improving mesh quality, mesh
adaptivity can be used to dynamically focus computational effort to resolve
sensitive features of a numerical solution. From \cite{Iske2004}
\begin{quote}
{\small In order to balance the method's approximation quality and its
computational costs effectively, adaptivity is an essential requirement,
especially when modelling multiscale phenomena.}
\end{quote}
For more on mesh adaptivity, see \cite{Babuska1978, Peraire1987, Pain2001}.

@@

\begin{figure}
  \includegraphics{main_figure27.pdf}
  \centering
  \captionsetup{width=.75\linewidth}
  \caption{Comparing straight sided meshes to a curved mesh when approximating
    the unit disc in \(\reals^2\).}
  \label{fig:curved-vs-straight-mesh}
\end{figure}

To allow for greater geometric flexibility and for high order of convergence,
curved mesh elements can be used in the finite element method. Though the
complexity of a method can steeply rise when allowing curved elements, the
trade for high-order convergence can be worth it. (See \cite{Wang2013} for
more on high-order CFD methods.) Curved meshes can typically
represent a given geometry with far fewer elements than a straight sided mesh
(for example, Figure~\ref{fig:curved-vs-straight-mesh}).
The increase in accuracy also allows for the use of fewer elements, which
in turn can also facilitate a reduction in the overall computation time.

>>>>

Lagrangian methods treat each point in the
physical domain as a ``particle'' which moves along a characteristic curve
over time and then monitor values associated with the particle (heat / energy,
velocity, pressure, density, concentration, etc.). They are an effective way
to solve PDEs, even with higher order or non-linear terms.
For example, the simple transport equation with a diffusion term
\begin{equation}
u_t + c u_x - \eps u_{xx} = 0
\end{equation}
has characteristics \(x(t) = x_0 + ct\) that only correspond to the
first order terms. The value then satisfies the
ODE \(\frac{d}{dt} u(x(t), t) = \eps u_{xx}\).

@@

To deal with distortion, one can allow the mesh to adapt in between time
steps. In addition to improving mesh quality, mesh
adaptivity can be used to dynamically focus computational effort to resolve
sensitive features of a numerical solution. From \cite{Iske2004}
\begin{quote}
{\small In order to balance the method's approximation quality and its
computational costs effectively, adaptivity is an essential requirement,
especially when modelling multiscale phenomena.}
\end{quote}
For more on mesh adaptivity, see \cite{Babuska1978, Peraire1987, Pain2001}.

@@

To allow for greater geometric flexibility and for high order of convergence,
curved mesh elements can be used in the finite element method. Though the
complexity of a method can steeply rise when allowing curved elements, the
trade for high-order convergence can be worth it. (See \cite{Wang2013} for
more on high-order CFD methods.) Curved meshes can typically
represent a given geometry with far fewer elements than a straight sided mesh.
The increase in accuracy also allows for the use of fewer elements, which
in turn can also facilitate a reduction in the overall computation time.
